Verifying Hierarchical Cache Coherence Protocols: a theorem-prover based modular, reusable proof

### 2014-02-05 paper/Intuition.tex
intuition

\section{Proof of MSI protocol being sound wrt Store atomicity}
\label{safety}

In this section, we present the proof structure for the soundness
property of our MSI-based cache coherence protocol of
Figure~\ref{trans}. Specifically, we formally reduce the proof of the
store atomicity theorem for the whole system to the proof of a set of
simple invariants by leveraging the ``intuitive'' justification of
correctness of our protocol.

%% This intuition
%% is not restricted to the MSI-based protocol;
%% Section~\ref{sec:Refinements} shows that it applies can apply to other
%% protocols.

Our invariants hold after any series of executions of the component
transactions of our design reachable from the initial state. We use
the term time $t$ to specify the global state reached after firing $t$
transitions.

While we have proofs in Coq of each step in this framework our
discussion will be mainly informal for brevity. A full description can
be found at~\xxx{MURALI PUT REFERENCE HERE}.

@@

The store atomicity is a whole system property. Intuitively our
protocol is correct because it guarantees that at most one node can
write at a time, and that any local cache that attempts to read has
the ``latest'' value. We can state this formally with the following 4
invariants about nodes:

\begin{defn}
\textit{clean}: A cache is said to be \clean{} for an address $a$ if and only if
the state of the cache for that address is at least \Sh{} and the
state of all its children is at most \Sh.
\end{defn}
\begin{inv}
At any time $t$, a cache $c$ which is clean for an address $a$ will have the most
up-to-date value for that address, \ie{}
\begin{enumerate}
\item $c.\data[a] = \initData(a)$ and no store request has been
  processed at any time $t_i$ such that $t_i < t$, or
\item There is a store request $q$ that was processed at time $t'$ such that
$t' < t$ and $a = q.\addrQ \wedge c.\data[a] = q.\dataQ$ and no other store
request $q'$ was processed at any time $t_i$ such that $t' < t_i < t \wedge a =
q'.\addrQ$.
\end{enumerate}
\label{latestValue}
\end{inv}

We use the definition of compatibility between two caches as follows:
\begin{defn}
\textit{compatibile}: Values of states $x_1$ and $x_2$ are compatible if and only if
either $x_1$ or $x_2$ is \Mo{}, then the other is \In.
\label{compatible}
\end{defn}

\begin{inv}
\textit{nonAncestorCompatible}: For two distinct caches $c_1$ and $c_2$ such
that neither is an ancestor of the other in the cache tree hierarchy, for each
address $a$, $c_1.\state[a]$ and $c_2.\state[a]$ are compatible.
\label{nonAncestorCompatible}
\end{inv}

\begin{inv}
\textit{processReq}: A load (store) request for an address at a leaf cache can
be processed only if it is at least in the \Sh{} (\Mo) state for that address.
\label{processReq}
\end{inv}

\begin{inv}
\textit{noReqAgain}:
\item For a leaf cache $c$, $c.\pos$ changes only on processing a request in
which case $c.\pos$ is incremented.
\label{noReqAgain}
\end{inv}

Given these invariants, we codify our intuition by showing that
Theorem~\fullref{storeAtomicity} follows naturally from these
invariants.  A store may happen only when leaf cache is in \Mo{} state
for that address (Invariant~\fullref{processReq}). Leaf caches cannot
be ancestors of any other node, so by Invariant
\fullref{nonAncestorCompatible}, if a leaf cache is in \Mo{} state, all
other leaf caches will be in \In{} state preventing the possibility of
load and store requests for the same address (by Invariant
\fullref{processReq}), showing Definition~\fullref{uniqStTimes} holds.

Given Invariant~\fullref{noReqAgain}, once a response has been produced
for a request $i$, the cache may subsequently only process $j^{th}$
request such that $j > i$. Thus there is at most one response to each
request, satisfying Definition~\fullref{uniqRespLabels}. A load request
may be processed only if a cache is at least in \Sh{} state (Invariant
\fullref{processReq}). As leaf caches have no children, a leaf cache in
at least in \Sh{} state for address $a$ is \clean for that address. A
load response supplies the data for that address present in the cache,
which, by Invariant~\fullref{lastestValue}, contains the ``latest
value''. Thus, the final condition for Theorem~\fullref{storeAtomicity}
is also satisfied. All that remains is to show that these properties hold.

@@

We can directly show that Invariants~\fullref{processReq} and
\fullref{noReqAgain} hold at the initial configuration and are
preserved through each atomic transition of our protocol
(Figure~\ref{trans}). Invariants~\fullref{uniqM} and
\fullref{latestValue} correctness rely on properties of the node
hierarchy. We can prove both using the following invariants on
parent-child relationships.

\begin{inv}
\textit{conservative}: The state of an address in a cache is never greater than
the corresponding entry in the parent's directory.
\label{conservative}
\end{inv}

\begin{inv}
\textit{localCompatibility}:
\begin{enumerate}
\item The state of a cache is never less than its directory entry for any of
its children.
\item Let $c_1$ and $c_2$ be distinct caches with the same parent $p$. Then,
$p.\dstate[c_1][a]$ and $p.\dstate[c_2][a]$ are compatible.
\end{enumerate}
\label{localCompatibility}
\end{inv}

@@

For any two caches $c$ and $p$, such that $p$ is an ancestor of $c$ in
the cache tree hierarchy, from Invariants \fullref{conservative} and
\fullref{localCompatibility}, we can show that for any address $a$,
$c.\state[a] \le p.\state[c][a]$. This is because the ancestor
relation is the reflective-transitive closure of the parent relation,
and Invariants \fullref{conservative} and the first part
\fullref{localCompatibility} of defines a $\ge$ relation between the
states of a parent and its child.

Any two caches $c_1, c_2$ neither of which are an ancestor of the
other will have a lowest common ancestor $x$ which is an ancestor of
both $c_1$ and $c_2$ and has two distinct children $x_1$ and $x_2$
such that they are the ancestors of $c_1$ and $c_2$ respectively. For
any address $a$, $x.\dstate[x_1][a]$ and $x.\dstate[x_1][a]$ are
compatible by the second part of
Invariant~\ref{localCompatibility}. From this, it straightaway follows
that $x_1.\state[a]$ and $x_2.\state[a]$ are compatible (from
Invariant~\ref{conservative}). From the previous paragraph, it follows
that $c_1$ and $c_2$ are also compatible. This proves
Invariant \fullref{nonAncestorCompatibility}.

We prove Invariant \fullref{latestValue} by strong induction on
time. Consider two cases: cache $c$ is already \clean{} for an address
$a$ at time $t$ or the contrary.  If \clean{}, then it has the latest
value at time $t$. Since none of its children's directory entries can
be in \Mo{}, all its descendants should be no greater than \Sh{} for
that address (as discussed above). Any non-ancestor of $c$, and
non-descendant of $c$ must be compatible (as discussed above). Since
$c$ is \clean, it is at least in the \Sh{} state, so compatibility
means that non-descendants can not be in \Mo{} state. All of $c$'s
ancestors are non-leaves, so they can not process any store
request. Therefore, no cache save $c$ may have process a store
request, which means that $c$ contains the latest value for address
$a$ at time $t+1$ if it was \clean{} at time $t$.

If $c$ was not clean at time $t$, it must have received data from
either its parent or its child.  As can be seen in Figure~\ref{trans},
whenever data is sent either from a parent to a child, or from a child
to the parent, the sender is \clean. By the induction hypothesis, it
means that the sender has the latest value for the address. Because of
Invariant~\ref{noTransitWrite}, no store request can be processed when
the data is in transit, which means $c$ will have the latest value for
address $a$ at time $t+1$.

@@

We present two basic invariants that the MSI protocol of
Figure~\ref{trans} obeys. In fact the protocol (\ie{} the
request/response message semantics) was designed to ensure the
following two invariants. We believe that most cache-coherence
protocols would end up obeying these two invariants; we show how MOSI,
for instance, obeys these invariants in
Section~\ref{sec:Refinements}. These two invariants together can prove
all the pair-wise properties of Section~\ref{pairwise}.

The transitions of the protocol are setup so that the following invariant holds:
\begin{inv}
\textit{noCross}: A response from a cache to its child for an address can not
be in transit while another response from the same child to the parent for the
same address is in transit.
\label{noCross}
\end{inv}

In addition, the following invariant must hold regarding the order of responses
between the same pair of nodes:
\begin{inv}
\textit{respFIFO}: Responses are received in the order in which they are sent,
for a source-destination pair, for the same address.
\end{inv}

The MSI-based protocol in Figure~\ref{trans} is such that any change in either
the state of a cache or its directory entry takes place only on sending or
receiving a response. The parent upgrades the corresponding directory entry on
sending a response to a child and the child downgrades its directory entry on
sending a response to the parent.

To prove Invariant \fullref{conservative} at some time $t$, consider the case
when a child cache $c$ has sent to or received from the parent $p$ some message
before $t$. Consider the last such message $m$ sent by or received at $c$ at
$t'$. Let's say $m$ is sent by $c$. Then $p$ can not have received any message
from $c$ after sending $m$ in order to not violate Invariant \fullref{noCross}.
Instead, if $c$ receives $m$ at $t'$, $p$ will not receive any message after
sending $m$ in order to not violate Invariants \fullref{noCross} and
\fullref{respFIFO}. Let $m$ be sent or received by $p$ at $t''$. In both cases,
$p.\dstate[c][a]$ at $t''+1$ will be equal to $c.\state[a]$ at $t'+1$ (because
the response messages sync up the next-state according to the transitions in
Figure \ref{trans}). Since $p$ can not receive any message between $t''+1$ and
$t$, it can only upgrade $p.\dstate[c][a]$. Since $c.\state[a]$ does not change
between $t'+1$ and $t$, Invariant \fullref{conservative} holds at $t$. If no
message has been sent or received by $c$ before $t$, then $p$
wouldn't have received any message sent by $c$ before $t$ as it means that the
message must be sent by $c$ before $t$. Since the initial states of the
directory and the child's state are both set to \In{}, the same argument holds
(in which the parent can only upgrade), thus maintaining Invariant
\fullref{conservative}.

To prove Invariant \fullref{localCompatibility}, it is enough to show that a
child $c$ upgrades $c.\state[a]$ on receiving a response for $a$ from its
parent $p$ and $p.\dstate[c][a]$ is downgraded on receiving a response for $a$
from $c$. If this is true, then Invariant \fullref{localCompatibility} will not
be violated on receiving a response. The transitions of Figure \ref{trans}
ensures that Invariant \fullref{localCompatibility} is not violated when sending
a response.

If the value of the state of a child at the time of sending a response is the
same as the value of the directory for that child at the parent at the time of
receiving the response, it follows straightaway that the parent downgrades its
directory on receiving a response from the child, since a child downgrades on
sending a response and the next-states are synced on receiving the response.
The proof for this follows exactly the same arguments presented above to prove
Invariant \fullref{conservative} -- we prove by considering the last message
sent or received at the child before $t$ (and the case when no message has been
sent or received).

Invariant \fullref{noTransitWrite} can be proved as follows. Consider a response
sent from a parent $p$ at time $t$ received by its child $c$ at time $t'$. No
other response can be received by the parent at time $t_p$ such that $t+1 \le
t_p \le t'$ to not violate Invariant \fullref{noCross}, so $p.\dstate[c][a]$ at
$t+1 \le p.\dstate[c][a]$ at $t'$, since the parent can only upgrade its
directory for $c$. Similarly, no response can be sent by the child at time
$t_c$ such that $t \le t_c \le t'$ for the same reason and hence $c.\state[a]$
at $t \le c.\state[a]$ at $t'$ since the child can only downgrade its state.
This means that during $t_p$ such that $t+1 \le t_p \le t'$, $p.\dstate[c][a]
> \In$ since the parent upgraded its directory for $c$ at $t$. Similarly,
during $t_c$ such that $t \le t_c \le t'$, $c.\state[a] < \Mo$ since the
child upgrades its state at $t'$. Using arguments similar to the proof of
Invariant \fullref{latestValue}, we can establish that no cache can be in \Mo{}
state for address $a$ when a response is in transit from $p$ to $c$.
Similarly, we can prove that no cache can be in \Mo{} state for address $a$
when a response is in transit for address $a$ from $c$ to $p$. Since data is in
transit at the same time as when the response is in transit, Invariant
\fullref{noTransitWrite} follows.

@@

%Invariant~\fullref{conservative} can be proved by

@@

%Invariant~\fullref{conservative} at any time $t$ for child cache $c$ and parent

>>>>

\section{Proof of MSI protocol being preserving Store atomicity}
\label{safety}

In this section, we present the structure of the proof of Theorem
\fullref{storeAtomicity} for a system implementing the MSI protocol of
Figure~\ref{trans}. We reduce the whole system proof to that of a set of
invariants between any parent-child pair. These invariants in turn depend on
exactly two invariants. Identifying these two basic invariants is one of the
main contributions of the paper; they also hold for other protocols like MOSI
(discussed in Section \ref{sec:Refinements}).

The invariants hold after any number of executions of the transactions starting
from the initial state. We use the term time $t$ to specify the global state
reached after firing $t$ transitions.

While we have proofs in Coq for each invariant our discussion will be mainly
informal for brevity. A full description can be found at~\xxx{MURALI PUT
REFERENCE HERE}.

@@

The store atomicity is a whole system property. Intuitively our
protocol is correct because it guarantees that at most one cache can
write at a time, and that any cache that attempts to read has
the ``latest'' value. We can state this formally with the following 4
invariants.

\begin{inv}
At any time $t$, a cache $c$ which is clean for an address $a$ will have the most
up-to-date value for that address, \ie{}
\begin{enumerate}
\item $c.\data[a] = \initData(a)$ and no store request $q'$ has been processed at
any time $t'$ such that $t' < t \wedge a = q'.\addrQ$, or
\item There is a store request $q$ that was processed at time $t_q$ such that
$t_q < t \wedge a = q.\addrQ \wedge c.\data[a] = q.\dataQ$ and no other store
request $q'$ was processed at any time $t'$ such that $t_q < t' < t \wedge a =
q'.\addrQ$.
\end{enumerate}
\label{latestValue}
\end{inv}
A clean cache is defined as follows.
\begin{defn}
\textit{clean}: A cache is said to be \clean{} for an address $a$ if and only if
the state of the cache for that address is at least \Sh{} and the directory 
state for all its children is at most \Sh.
\end{defn}

\begin{inv}
\textit{nonAncestorCompatible}: For two distinct caches $c_1$ and $c_2$ such
that neither is an ancestor of the other in the cache tree
hierarchy (where ancestor relation is the reflexive-transitive closure of the parent relation), for each
address $a$, $c_1.\state[a]$ and $c_2.\state[a]$ are \textit{compatible}.
\label{nonAncestorCompatible}
\end{inv}
Compatibility of states is defined as follows.
\begin{defn}
\textit{compatibile}: Values of states $x_1$ and $x_2$ are \textit{compatible} iff
either $x_1$ or $x_2$ is \Mo{}, then the other is \In. Note that any two states $y_1 \le x_1$ and $y_2 \le x_2$ are also compatible if $x_1, x_2$ are compatible.
\label{compatible}
\end{defn}

%\begin{inv}
%\textit{processReq}: Load and store requests can be processed at a leaf cache
%only if it is at least in the \Sh{} and \Mo{} states, respectively, for that
%address.
%\label{processReq}
%\end{inv}
%
%\begin{inv}
%\textit{noReqAgain}:
%\item For a leaf cache $c$, $c.\pos$ changes only on processing a request. In
%that case, $c.\pos$ gets incremented.
%\label{noReqAgain}
%\end{inv}

Given these invariants, we will show how Theorem~\fullref{storeAtomicity}
follows. From the transitions of Figure \ref{trans}, a store may happen only
when a leaf cache is in \Mo{} state for that
address%(Invariant~\textit{processReq}).
Leaf caches cannot be ancestors of any
other node, so by Invariant \fullref{nonAncestorCompatible}, if a leaf cache is
in \Mo{} state, all other leaf caches will be in \In{} state preventing the
possibility of processing load and store requests for the same address at the
same time. Thus, Definition~\fullref{uniqStTimes} holds.

Once a response has been produced for a request $i$, the cache increments the
counter for the request it processes next. Thus there is at most one response
to each request, satisfying Definition~\fullref{uniqRespLabels}. As leaf caches
have no children, a leaf cache in at least \Sh{} state for address $a$ is
\clean{} for that address. Since processing a load request requires the cache
to be at least in the \Sh{} state, its response, which supplies the data for
that address present in the cache, supplies the latest value by
Invariant~\fullref{lastestValue}.  Thus, the final condition for
Theorem~\fullref{storeAtomicity} is also satisfied. All that remains is to show
how these invariants hold.

@@

Correctness of Invariants \fullref{uniqM} and \fullref{latestValue} can be
proved using the following invariants on a parent-child pair.

\begin{inv}
\textit{conservative}: The state of an address in a cache is never greater than
the corresponding entry in its parent's directory.
\label{conservative}
\end{inv}

\begin{inv}
\textit{localCompatibility}:
\begin{enumerate}
\item The state of a cache is never less than its directory entry for any of
its children.
\item Let $c_1$ and $c_2$ be distinct caches with the same parent $p$. Then,
$p.\dstate[c_1][a]$ and $p.\dstate[c_2][a]$ are \textit{compatible}.
\end{enumerate}
\label{localCompatibility}
\end{inv}

@@

For any two caches $c$ and $p$, such that $p$ is an ancestor of $c$ in
the cache tree hierarchy,

Invariant \fullref{conservative} and the first part of Invariant
\fullref{localCompatibility} defines a $\ge$ relation between the states of a
parent and its child for any address.  Since the ancestor relation is the
reflexive-transitive closure of the parent relation, the $\ge$ relation is
preserved between the states of two caches $p$ and $c$ where $p$ is the
ancestor of $c$.

Any two caches $c_1, c_2$ neither of which are an ancestor of the other has a
lowest common ancestor $x$ which is an ancestor of both $c_1$ and $c_2$. $x$
has two distinct children $x_1$ and $x_2$ such that they are the ancestors of
$c_1$ and $c_2$ respectively. For any address $a$, $x.\dstate[x_1][a]$ and
$x.\dstate[x_1][a]$ are compatible by the second part of
Invariant~\fullref{localCompatibility}. It follows that $x_1.\state[a]$ and
$x_2.\state[a]$ are compatible since these values are smaller than the
respective directory values.  From the previous paragraph about the relation
between the states of a cache and its ancestor, it follows that $c_1$ and $c_2$
are also compatible. This proves Invariant \fullref{nonAncestorCompatible}.

We prove Invariant \fullref{latestValue} by strong induction on time. Consider
two cases: a) cache $c$ is already \clean{} for an address $a$ at time $t$ or
b) the contrary.  If \clean{}, then it has the latest value at time $t$. Since
none of its children's directory entries can be in \Mo{}, all its descendants
should be no greater than \Sh{} for that address (because of Invariant
\fullref{conservative} and the fact that $\ge$ relation is preserved for the
state of a cache and that of its ancestor). Any non-ancestor of $c$, and
non-descendant of $c$ must be compatible (as discussed in the previous
paragraph).  Since $c$ is \clean, it is at least in the \Sh{} state, so
compatibility means that non-descendants can not be in \Mo{} state. All of
$c$'s ancestors are non-leaves, so they can not process any store request.
Therefore, no cache save $c$ may have process a store request, which means that
$c$ contains the latest value for address $a$ at time $t+1$ if it was \clean{}
at time $t$.

If $c$ was not clean at time $t$, it must have received data from either its
parent or its child.  As can be seen in Figure~\ref{trans}, whenever data is
sent either from a parent to a child, or from a child to the parent, the sender
is \clean. By the induction hypothesis, it means that the sender has the latest
value for the address. Because of Invariant~\ref{noTransitWrite}, no store
request can be processed when the data is in transit, which means $c$ will have
the latest value for address $a$ at time $t+1$. This establishes Invariant
\fullref{latestValue}.

@@

We present two basic invariants that the MSI protocol of Figure~\ref{trans}
obeys. In fact the request/response message semantics was designed to satisfy
the following two invariants. We believe that most cache-coherence protocols
would end up obeying these two invariants. With two invariants we can
prove all the pair-wise properties of Section~\ref{pairwise}.

\begin{inv}
\textit{noCross}: A response from a cache to its child for an address can not
be in transit while another response from the same child to the parent for the
same address is in transit.
\label{noCross}
\end{inv}

\begin{inv}
\textit{respFIFO}: Responses are received in the order in which they are sent,
for a source-destination pair, for the same address.
\end{inv}

The MSI-based protocol in Figure~\ref{trans} is such that any change in either
the state of a cache or its directory entry takes place only on sending or
receiving a response. The parent upgrades the corresponding directory entry on
sending a response to a child and the child downgrades its state on
sending a response to the parent.

To prove Invariant \fullref{conservative} at some time $t$, consider the case
when a child cache $c$ has sent to or received from the parent $p$ some message
before $t$. Consider the last such message $m$ sent by or received at $c$ at
$t'$. Let's say it is sent by $c$ at $t'$, not received. Then $p$ can not have
received any message from $c$ after sending $m$ and before $t$ in order to not
violate Invariant \fullref{respFIFO}.  Instead, if $c$ receives $m$ at $t'$,
$p$ will not receive any message after sending $m$ and before $t$ in order to
not violate Invariant \fullref{noCross}. Thus, $p$ will not receive any message
from $c$ after sending or receiving $m$ and before $t$.  Let $t''$ be the time
at which $p$ has sent or received $m$. Whether $p$ sends or receives $m$,
$p.\dstate[c][a]$ at $t''+1$ will be equal to $c.\state[a]$ at $t'+1$ because
the response messages sync up the next-state according to the transitions in
Figure \ref{trans}. Since $p$ can not receive any message between $t''+1$ and
$t$, it can only upgrade $p.\dstate[c][a]$. $c.\state[a]$ does not change
between $t'+1$ and $t$ as it never changes state. Therefore, Invariant
\fullref{conservative} holds at $t$.

If no message has been sent or received by $c$ before $t$, then $p$ wouldn't
have received any message sent by $c$ before $t$. So $p.\dstate[c][a]$ at time
$t \ge p.\dstate[c][a]$ at time $0$ . Since the initial values of the directory
and the child's state are both set to \In{} Invariant \textit{conservative}
holds.

To prove Invariant \fullref{localCompatibility}, it is enough to show that a
$c.\state[a]$ is upgraded on receiving a response for $a$ from $c$'s parent $p$
and $p.\dstate[c][a]$ is downgraded on receiving a response for $a$ from $c$.
If this is true, then Invariant \fullref{localCompatibility} will not be
violated on receiving a response. The transitions of Figure \ref{trans} ensures
that Invariant \fullref{localCompatibility} is not violated when sending a
response. Since whenever the state or directory changes, the appropriate
response is sent or received, Invariant \fullref{localCompatibility} holds.

If the value of the state of a child at the time of sending a response is the
same as the value of the directory for that child at the parent at the time of
receiving the response, it follows straightaway that the parent downgrades its
directory on receiving a response from the child. This is because a child
downgrades on sending a response and the next-states are synced on receiving
the response.  This proof uses exactly the same arguments presented above to
prove Invariant \fullref{conservative} -- we prove by considering the last
message sent or received at the child before $t$ (and the case when no message
has been sent or received). Similarly, we can show that a child upgrades its
state on receiving a response, satisfying the conditions in the previous paragraph.

Invariant \fullref{noTransitWrite} can be proved as follows. Consider a
response sent from a parent $p$ at time $t$ received by its child $c$ at time
$t'$. No other response can be received by the parent at time $t_p$ such that
$t+1 \le t_p \le t'$ in order to not violate Invariant \fullref{noCross}, so
$p.\dstate[c][a]$ at $t+1 \le p.\dstate[c][a]$ at $t'$, since the parent can
only upgrade its directory for $c$. Similarly, no response can be sent by the
child at time $t_c$ such that $t \le t_c \le t'$ for the same reason and hence
$c.\state[a]$ at $t \le c.\state[a]$ at $t'$ since the child can only downgrade
its state.  This means that during $t_p$ such that $t+1 \le t_p \le t'$,
$p.\dstate[c][a] > \In$ and (hence $p.\state[a] > \In$ by the first part of
Invariant \fullref{localCompatibility}) since the parent upgraded its directory
for $c$ at $t$.  Similarly, during $t_c$ such that $t \le t_c \le t'$,
$c.\state[a] < \Mo$ since the child upgrades its state at $t'$. We have already
shown that (in the proof of Invariant \fullref{latestValue}) if any cache is
not in \In{} state, no non-descendent cache can process a store request. In
this case, during the times between $t$ and $t'$, $p$ is not in \In{} state.
Among $p$'s directory entries, all of them save the entry for $c$ is not in
\Mo{} state, so none of the descendents of $p$'s children, save $c$'s
descendents can process a store request. During the times between $t$ and $t'$,
$c$'s state is $< \Mo{}$, so neither $c$ nor its descendents can process a store
request, proving Invariant \fullref{noTransitWrite}.

@@

%Invariant~\textit{conservative} can be proved by

@@

%Invariant~\textit{conservative} at any time $t$ for child cache $c$ and parent
